The letter

### 2010-07-01 ltx/PLoS/LaTeX_Manuscript.tex
missed a couple of cross-refs that need removal

\subsection*{Implications for Experiment Design}
As seen in Section~\ref{sec:state_and_param_results}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.

The frequency analysis presented in Section~\ref{SpectralAnalysisSection} specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics. Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing. In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data. This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.

>>>>

\subsection*{Implications for Experiment Design}
As seen in Figure~\ref{fig:Parameters}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.

The frequency analysis specify the minimum sensor arrangement that is required to capture the dominant cortical dynamics. Importantly, these new tools can also be used to design electrophysiological recording systems to avoid spatial aliasing. In addition, the frequency analysis highlights the relationship between the spatial width of the sensors and the information in the data. This analysis is becoming increasingly relevant as recording systems are becoming more sophisticated with higher density electrodes~\cite{Brinkmann2009}.
